---
title: "IQM measures"
author: "Heejung Jung"
date: "`r Sys.Date()`"
output: html_document
---

Here, we plot the FD means, DVARs and tSNR from spacetop individual tasks.
For FD means, we also plot the UKB task FD values.

```{r include=FALSE}
library(ggplot2)
library(raincloudplots)
library(gghalves)
library(plyr); library(dplyr)

# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/R_rainclouds.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/summarySE.R")
# source("/Users/h/Documents/projects_local/RainCloudPlots/tutorial_R/simulateData.R")
source("https://gist.githubusercontent.com/benmarwick/2a1bb0133ff568cbe28d/raw/fb53bd97121f7f9ce947837ef1a4c65a73bffb3f/geom_flat_violin.R")

library(r2mlm)
file.sources = list.files(c("/Users/h/Documents/projects_local/cue_expectancy/scripts/step02_R/utils"),
                          pattern="*.R", 
                          full.names=TRUE, 
                          ignore.case=TRUE)
sapply(file.sources,source,.GlobalEnv)

```

## functions for plots

```{r}
calculate_factor_range <- function(data, factor_column, border_levels) {
    if (is.null(border_levels) || length(border_levels) == 0) {
        return(NULL)
    }

    levels_to_include <- as.character(border_levels)
    factor_levels <- levels(factor(data[[factor_column]]))
    positions <- which(factor_levels %in% levels_to_include)

    if (length(positions) == 0) {
        return(NULL)
    }

    # Adjust xmin and xmax based on position in the factor levels
    n_levels <- length(factor_levels)
    padding <- 0.5
    xmin_range <- ifelse(min(positions) == 1, min(positions) - padding, min(positions) - padding / 2)
    xmax_range <- ifelse(max(positions) == n_levels, max(positions) + padding, max(positions) + padding / 2)

    return(list(xmin = xmin_range, xmax = xmax_range))
}

```

### plot function half rainclouds boxplot


```{r}
plot_halfrainclouds_onefactor <- function(subjectwise,
                                          groupwise,
                                          iv,
                                          subjectwise_mean,
                                          group_mean,
                                          se,
                                          subject,
                                          ggtitle,
                                          title,
                                          xlab,
                                          ylab,
                                          taskname,
                                          ylim,
                                          w,
                                          h,
                                          dv_keyword,
                                          color,
                                          border_levels=NULL, 
                                          border_color=NULL,
                                          save_fname) {
  
  # ----------------------------------------------------------------------------
  #  initialize ggplot
  # ----------------------------------------------------------------------------
  
  g <- ggplot(data = subjectwise,
              aes(
                y = .data[[subjectwise_mean]],
                x = factor(.data[[iv]]),
                fill = factor(.data[[iv]])
              )) +
    coord_cartesian(ylim = ylim, expand = TRUE) + 
    scale_x_discrete() # since x is a factor, we'll indicate it as discrete
  # ----------------------------------------------------------------------------
  #  rectangle around specific levels (UKB data)
  # ----------------------------------------------------------------------------
      if (!is.null(border_levels)) {
    levels_to_include <- as.character(border_levels)
    factor_levels <- levels(factor(subjectwise[[iv]]))
    positions <- which(factor_levels %in% levels_to_include)

    # Calculate the range
    if (length(positions) == 1) {
        # For a single level, return the exact position
        xmin_range <- positions - 0.5
        xmax_range <- positions + 0.5
    } else {
        # For multiple levels, return the min and max positions
        xmin_range <- min(positions) - 0.5
        xmax_range <- max(positions) + 0.5
    }

  # Adding a rectangle annotation covering the range
  g <- g +
    annotate(
      "rect",
      xmin = as.numeric(xmin_range), xmax = as.numeric(xmax_range),
      ymin = -Inf, ymax = Inf,
      fill = border_color, alpha = 0.1
    ) +
    geom_vline(
      xintercept = xmax_range,
      linetype = "dashed", color = border_color, size = .5
    )
    }
  # ----------------------------------------------------------------------------
  #  violin plots
  # ----------------------------------------------------------------------------
  g <- g +  geom_half_violin(
    data = subjectwise,
    aes(fill = factor(.data[[iv]])),
    side = 'r',
    position = 'dodge',
    adjust = 1.5,
    trim = FALSE,
    alpha = .9,
    colour = NA,
    width = 1.5
  ) +
    
    geom_point(
      aes(
        # group = .data[[subject]],
        x = as.numeric(as.factor(.data[[iv]])) - .2 ,
        y = .data[[subjectwise_mean]],
        color = factor(.data[[iv]])
      ),
      position = position_jitter(width = .05),
      size = .1,
      alpha = 0.2,
    ) +
    
    geom_boxplot(
      data = subjectwise,
      aes(x = .data[[iv]],
          y = .data[[subjectwise_mean]],
          fill = .data[[iv]]),
      side = "r",
      outlier.shape = NA,
      alpha = 0.8,
      width = .1,
      notch = FALSE,
      notchwidth = 0,
      varwidth = FALSE,
      colour = "black",
      errorbar.draw = FALSE
    ) +
    
  # ----------------------------------------------------------------------------
  #  legend stuff
  # ----------------------------------------------------------------------------
    expand_limits(x = 2.8) +
    guides(color = "none") +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_bw()
  
  ggsave(save_fname, width = w, height = h)
  return(g)
}

```


### plot pointrange function half rainclouds pointrange
```{r}
plot_halfrainclouds_pointrange <- function(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w, h, dv_keyword, color,border_levels=NULL, border_color=NULL, save_fname) {
  print(names(subjectwise))
  print(names(groupwise))
  g <- ggplot(
    data = subjectwise,
    aes(
      y = .data[[subjectwise_mean]],
      x = factor(.data[[iv]]),
      fill = factor(.data[[iv]])
    )
  ) +
    
    coord_cartesian(ylim = ylim, expand = TRUE) + scale_x_discrete()

  # ----------------------------------------------------------------------------
  #  rectangle around UKB data
  # ----------------------------------------------------------------------------
    # factor_levels <- levels(factor(subjectwise[[iv]]))
    # position_ukb_faces <- which(factor_levels == "UKB faces")
    # position_ukb_rest <- which(factor_levels == "UKB rest")
    # xmin_range <- min(position_ukb_faces, position_ukb_rest) - 0.5
    # xmax_range <- max(position_ukb_faces, position_ukb_rest) + 0.5
    # Ensure the input levels are a character vector
      if (!is.null(border_levels)) {
    levels_to_include <- as.character(border_levels)
    factor_levels <- levels(factor(subjectwise[[iv]]))
    positions <- which(factor_levels %in% levels_to_include)

    # Calculate the range
    if (length(positions) == 1) {
        # For a single level, return the exact position
        xmin_range <- positions - 0.5
        xmax_range <- positions + 0.5
    } else {
        # For multiple levels, return the min and max positions
        xmin_range <- min(positions) - 0.5
        xmax_range <- max(positions) + 0.5
    }

  # Adding a rectangle annotation covering the range
  g <- g +
    annotate(
      "rect",
      xmin = as.numeric(xmin_range), xmax = as.numeric(xmax_range),
      ymin = -Inf, ymax = Inf,
      fill = border_color, alpha = 0.1
    ) +
    geom_vline(
      xintercept = xmax_range,
      linetype = "dashed", color = border_color, size = .5
    )
      }

# ----------------------------------------------------------------------------
#  violin plot
# ----------------------------------------------------------------------------  
   g <- g+ geom_half_violin(
      aes(fill = factor(.data[[iv]])),
      side = 'r',
      position = 'dodge',
      adjust = 1.5,
      trim = FALSE,
      alpha = .9,
      colour = NA,
      width=1.5
    ) +

  geom_point(
    data = subjectwise, 
    aes(
      
      x = as.numeric(as.factor(.data[[iv]])) - .15 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = .1,
    alpha = 0.7,
  ) + 

    
    geom_pointrange(data = groupwise,
                    aes(fill = factor(.data[[iv]]),
                        # group = factor(.data[[iv]]),
                        y = .data[[group_mean]],
                        x = factor(.data[[iv]]),
                        ymin = (.data[[group_mean]] - .data[[se]]),
                        ymax = (.data[[group_mean]] + .data[[se]])
                        ),
                   position = position_dodge(width = 0.1),
                   size = 0.1
                   
                    ) + 

# ----------------------------------------------------------------------------
#  legend
# ----------------------------------------------------------------------------
    expand_limits(x = 2.8) +
    #guides(fill = "none") +
    guides(color = "none") +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_bw() 

  # ggsave(save_fname, width = w, height = h)
  return(g)
}

```

```{r}
plot_violin_onefactor <- function(subjectwise, groupwise, iv,
                                      subjectwise_mean, group_mean, se, subject,
                                      ggtitle, title, xlab, ylab, taskname, ylim,
                                      w, h, dv_keyword, color, save_fname) {
  g <- ggplot(
    data = subjectwise,
    aes(
      y = .data[[subjectwise_mean]],
      x = factor(.data[[iv]]),
      fill = factor(.data[[iv]])
    )
  ) +
    coord_cartesian(ylim = ylim, expand = TRUE) +

    geom_violin(
      aes(fill = factor(.data[[iv]])),
      side = 'r',
      position = 'dodge',
      adjust = 1.5,
      trim = FALSE,
      alpha = .3,
      colour = NA
    ) +

  geom_point(
    aes(
      # group = .data[[subject]],
      x = as.numeric(as.factor(.data[[iv]])) - .15 ,
      y = .data[[subjectwise_mean]],
      color = factor(.data[[iv]])
    ),
    position = position_jitter(width = .05),
    size = 2,
    alpha = 0.7,
  ) +

    geom_boxplot(
      data = subjectwise,
      aes(x = .data[[iv]],
          y = .data[[subjectwise_mean]],
          fill = .data[[iv]]),
      side = "r",
      outlier.shape = NA,
      alpha = 0.8,
      width = .1,
      notch = FALSE,
      notchwidth = 0,
      varwidth = FALSE,
      colour = "black",
      # errorbar.draw = FALSE
    ) +


    # legend stuff ________________________________________________________ # nolint
    expand_limits(x = 2.8) +
    #guides(fill = "none") +
    guides(color = "none") +
    guides(fill = guide_legend(title = title)) +
    scale_fill_manual(values = color) +
    scale_color_manual(values = color) +
    ggtitle(ggtitle) +
    xlab(xlab) +
    ylab(ylab) +
    theme_bw() 

  ggsave(save_fname, width = w, height = h)
  return(g)
}

```


## load data
```{r}
df <- read.csv("/Users/h/Documents/projects_local/spacetop-prep/spacetop_prep/qcplot/iqmvalues/iqmvalues.csv")
```

## FDmean
```{r}
df$task_factor <- factor(df$task)
subject <- "sub"
model_iv <- "task_factor"
dv <- "fd_mean"
subjectwise <- meanSummary(df,c(subject, model_iv), dv)

groupwise <- summarySEwithin(
  data=subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv),
  idvar = subject
)

df$task_factor <- factor(df$task)
subject <- "sub"
# model_iv <- "task_factor"
dv <- "fd_mean"
subjectwise_all <- meanSummary(df,c(subject), dv)
subjectwise_all$task_factor <- "all tasks"

groupwise_all <- summarySE(
  data=subjectwise_all,
  measurevar = "mean_per_sub",
  # withinvars = subject,
  # groupvars = subject
)
colnames(groupwise_all)
library(dplyr)
# groupwise_all <- groupwise_all %>% rename("task_factor" = ".id")
colnames(groupwise_all)[1] <- "task_factor"
groupwise_all$task_factor <- "all tasks"

# Find common columns
group_common_columns <- intersect(names(groupwise), names(groupwise_all))

# Subset both data frames to only the common columns
df1_common <- groupwise[group_common_columns]
df2_common <- groupwise_all[group_common_columns]

# Row-bind the subsets
groupwise_combined <- rbind(df1_common, df2_common)
subjectwise_combined <- rbind(subjectwise, subjectwise_all)

```
## UKbiobank FDmean

```{r}
ukb <- read.csv("/Users/h/Documents/projects_local/spacetop-prep/spacetop_prep/qcplot/iqmvalues/fd-mean_ukb.csv")

ukb$task_factor[ukb$task == "faces"] <- "UKB faces"
ukb$task_factor[ukb$task == "rest"] <- "UKB rest"
ukb$task_factor <- factor(ukb$task_factor)
subject <- "sub"
model_iv <- "task_factor"
dv <- "fd_mean"
ukb_subjectwise <- meanSummary(ukb, c(subject, model_iv), dv)


ukb_groupwise <- summarySE(
  data=ukb_subjectwise,
  measurevar = "mean_per_sub",
  groupvars = c("task_factor"),
  na.rm=TRUE
  # na.rm = na.rm
  # betweenvars = "subject",
  # withinvars = c(model_iv),
  # idvar = subject
)
colnames(ukb_groupwise)[1] <- "task_factor"
g <- plot_halfrainclouds_onefactor(
  ukb_subjectwise,
  ukb_groupwise,
  iv="task_factor",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_mean",
  se = "se",
  subject = "sub",
  ggtitle = "UKB and Spacetop FDmean across tasks",
  title="title",
  xlab="fd mean",
  ylab="task",
  taskname="spacetop",
  ylim=c(0,.9),
  w=5,
  h=.5,
  dv_keyword="iqm",
  color=c("#6496BF","#3A7F7E","#996666","#E6A74B","#D85038", "#5A0B4D", "black", "navy", "purple"),
  save_fname="./iqm.png"
)
g + coord_flip() + 
  ylim(0,.9) + theme_classic()+ ylab("Framewise displacement (FD)") + xlab("task") +
theme(
      plot.title = element_text(size = 20), # Adjust plot title size
      axis.title = element_text(size = 20), # Adjust axis titles size
      axis.text = element_text(size = 15),  # Adjust axis text size
      legend.title = element_text(size = 15), # Adjust legend title size
      legend.text = element_text(size = 10)  # Adjust legend text size
      
    ) +
theme(text = element_text(size = 20))

ggsave(save_fname, width = w, height = h)
```

## Fig 0. ukbiobank + spacetop combined


```{r}
# ----------------------------------------------------------------------------
#  Find common columns across dataframes for merging
# ----------------------------------------------------------------------------
fd.group.commoncolumn <- intersect(names(ukb_groupwise),
          names(groupwise_combined)
)

fd.subject.commoncolumn <- intersect(names(ukb_subjectwise),
          names(subjectwise_combined)
)
ukb.groupwise.common <- ukb_groupwise[fd.group.commoncolumn]
st.groupwise.common <- groupwise_combined[fd.group.commoncolumn]

ukb.subjectwise.common <- ukb_subjectwise[fd.subject.commoncolumn]
st.subjectwise.common <- subjectwise_combined[fd.subject.commoncolumn]


# ----------------------------------------------------------------------------
#  rstack dataframes across spacetop and ukbiobank
# ----------------------------------------------------------------------------
fd.groupwise.ukbst<- rbind(ukb.groupwise.common, st.groupwise.common)
fd.subjectwise.ukbst <- rbind(ukb.subjectwise.common, st.subjectwise.common)
fd.subjectwise.ukbst$task_ordered <- factor(fd.subjectwise.ukbst$task_factor, 
                             levels = c(  "UKB rest", "UKB faces", "all tasks","social","shortvideo", "narratives","fractional","faces", "alignvideo"))
fd.groupwise.ukbst$task_ordered <- factor(fd.groupwise.ukbst$task_factor, 
                             levels = c(  "UKB rest", "UKB faces", "all tasks","social","shortvideo", "narratives","fractional","faces", "alignvideo"))

# ----------------------------------------------------------------------------
#  plot
# ----------------------------------------------------------------------------
g <- plot_halfrainclouds_onefactor(
  fd.subjectwise.ukbst,
  fd.groupwise.ukbst,
  iv="task_ordered",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_mean",
  se = "se",
  subject = "sub",
  ggtitle = "UKB and Spacetop FDmean across tasks",
  title="title",
  xlab="Framewise displacement (FD)",
  ylab="Task",
  taskname="spacetop",
  ylim=c(0,.9),
  w=5,
  h=5,
  dv_keyword="iqm",
  color=c("gray", "gray","#333333", "#6496BF", "#4f8b9e", "#3A7F7E", 
              # "#6a7272",
              "#996666","#c08658","#e6a74b", "#E18745", "#5A0B4D" ),
  border_color = "gray", 
  border_level = c("UKB faces", "UKB rest"),
  save_fname="./fd_ukb_spacetop.png"
)


# ----------------------------------------------------------------------------
#  color palettes
# ----------------------------------------------------------------------------
# color = c("black","gray", "#6496BF","#3A7F7E","#996666","#E6A74B","#D85038", "#5A0B4D" )
# batlow


# ----------------------------------------------------------------------------
#  plot vertically and make transparent
# ----------------------------------------------------------------------------
g <- g + coord_flip() + 
  ylim(0,.9) + theme_classic()+ ylab("Framewise displacement (FD)") + xlab("Task") +
theme(
      plot.title = element_text(size = 15), # Adjust plot title size
      axis.title = element_text(size = 15), # Adjust axis titles size
      axis.text = element_text(size = 12),  # Adjust axis text size
      legend.title = element_text(size = 15), # Adjust legend title size
      legend.text = element_text(size = 10)  # Adjust legend text size
      
    ) +
theme(text = element_text(size = 20)) + 
  theme(
    panel.background = element_rect(fill='transparent'), #transparent panel bg
    plot.background = element_rect(fill='transparent', color=NA), #transparent plot bg
    panel.grid.major = element_blank(), #remove major gridlines
    panel.grid.minor = element_blank(), #remove minor gridlines
    legend.background = element_rect(fill='transparent'), #transparent legend bg
    legend.box.background = element_rect(fill='transparent') #transparent legend panel
  )   

g
# ggsave(save_fname, g, width = w, height = h)
ggsave("/Users/h/Dropbox/projects_adobe/spacetop_datapaper/iqm_fd.png", plot = g, width = 8, height = 5, dpi = 600)
```




## UKbiobank FDmean

```{r}
ukb.concat <- read.csv("/Users/h/Documents/projects_local/spacetop-prep/spacetop_prep/qcplot/iqmvalues/fd-mean_ukb.csv")

ukb.concat$task_factor[ukb.concat$task == "faces"] <- "UKB"
ukb.concat$task_factor[ukb.concat$task == "rest"] <- "UKB"
ukb.concat$task_factor <- factor(ukb.concat$task_factor)
subject <- "sub"
model_iv <- "task_factor"
dv <- "fd_mean"
ukb_subjectwise <- meanSummary(ukb.concat, c(subject, model_iv), dv)


ukb_groupwise <- summarySE(
  data=ukb_subjectwise,
  measurevar = "mean_per_sub",
  groupvars = c("task_factor"),
  na.rm=TRUE
  # na.rm = na.rm
  # betweenvars = "subject",
  # withinvars = c(model_iv),
  # idvar = subject
)
colnames(ukb_groupwise)[1] <- "task_factor"
g <- plot_halfrainclouds_onefactor(
  ukb_subjectwise,
  ukb_groupwise,
  iv="task_factor",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_mean",
  se = "se",
  subject = "sub",
  ggtitle = "UKB and Spacetop FDmean across tasks",
  title="title",
  xlab="fd mean",
  ylab="task",
  taskname="spacetop",
  ylim=c(0,.9),
  w=5,
  h=.5,
  dv_keyword="iqm",
  color=c("#6496BF","#3A7F7E","#996666","#E6A74B","#D85038", "#5A0B4D", "black", "navy", "purple"),
  save_fname="./iqm.png"
)
g + coord_flip() + 
  ylim(0,.9) + theme_classic()+ ylab("Framewise displacement (FD)") + xlab("task") +
theme(
      plot.title = element_text(size = 20), # Adjust plot title size
      axis.title = element_text(size = 20), # Adjust axis titles size
      axis.text = element_text(size = 15),  # Adjust axis text size
      legend.title = element_text(size = 15), # Adjust legend title size
      legend.text = element_text(size = 10)  # Adjust legend text size
      
    ) +
theme(text = element_text(size = 20))

# ggsave(save_fname, width = w, height = h)
```

## Fig 1. ukbiobank + spacetop combined


```{r}
# ----------------------------------------------------------------------------
#  Find common columns across dataframes for merging
# ----------------------------------------------------------------------------
fd.group.commoncolumn <- intersect(names(ukb_groupwise),
          names(groupwise_combined)
)

fd.subject.commoncolumn <- intersect(names(ukb_subjectwise),
          names(subjectwise_combined)
)
ukb.groupwise.common <- ukb_groupwise[fd.group.commoncolumn]
st.groupwise.common <- groupwise_combined[fd.group.commoncolumn]

ukb.subjectwise.common <- ukb_subjectwise[fd.subject.commoncolumn]
st.subjectwise.common <- subjectwise_combined[fd.subject.commoncolumn]


# ----------------------------------------------------------------------------
#  rstack dataframes across spacetop and ukbiobank
# ----------------------------------------------------------------------------
fd.groupwise.ukbst<- rbind(ukb.groupwise.common, st.groupwise.common)
fd.subjectwise.ukbst <- rbind(ukb.subjectwise.common, st.subjectwise.common)
fd.subjectwise.ukbst$task_ordered <- factor(fd.subjectwise.ukbst$task_factor, 
                             levels = c(  "UKB", "all tasks","social","shortvideo", "narratives","fractional","faces", "alignvideo"))
fd.groupwise.ukbst$task_ordered <- factor(fd.groupwise.ukbst$task_factor, 
                             levels = c( "UKB", "all tasks","social","shortvideo", "narratives","fractional","faces", "alignvideo" ))

# ----------------------------------------------------------------------------
#  plot
# ----------------------------------------------------------------------------
g <- plot_halfrainclouds_onefactor(
  fd.subjectwise.ukbst,
  fd.groupwise.ukbst,
  iv="task_ordered",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_mean",
  se = "se",
  subject = "sub",
  ggtitle = "UKB and Spacetop FDmean across tasks",
  title="title",
  xlab="Framewise displacement (FD)",
  ylab="Task",
  taskname="spacetop",
  ylim=c(0,.9),
  w=5,
  h=5,
  dv_keyword="iqm",
  color=c("#333333", "#9300ff", "#6496BF", "#4f8b9e", "#3A7F7E", 
              # "#6a7272",
              "#996666","#c08658","#e6a74b", "#E18745", "#5A0B4D" ),
  border_levels = c("UKB"),
  border_color = "#920717",
  save_fname="./fd_ukb_spacetop.png"
)


# ----------------------------------------------------------------------------
#  color palettes
# ----------------------------------------------------------------------------
# color = c("black","gray", "#6496BF","#3A7F7E","#996666","#E6A74B","#D85038", "#5A0B4D" )
# batlow


# ----------------------------------------------------------------------------
#  plot vertically and make transparent
# ----------------------------------------------------------------------------
g <- g + coord_flip() +
  ylim(0, .9) + theme_classic() + ylab("Framewise displacement (FD)") + xlab("Task") +
  theme(
    plot.title = element_text(size = 15),      # Adjust plot title size
    axis.title = element_text(size = 15),      # Adjust axis titles size
    axis.text = element_text(size = 12),       # Adjust axis text size
    legend.title = element_text(size = 15),    # Adjust legend title size
    legend.text = element_text(size = 10)      # Adjust legend text size
    
  ) +
  theme(text = element_text(size = 20)) +
  theme(
    panel.background = element_rect(fill = 'transparent'),     # transparent panel bg
    plot.background = element_rect(fill = 'transparent', color = NA),    # transparent plot bg
    panel.grid.major = element_blank(),                        # remove major gridlines
    panel.grid.minor = element_blank(),                        # remove minor gridlines
    legend.background = element_rect(fill = 'transparent'),    # transparent legend bg
    legend.box.background = element_rect(fill = 'transparent') # transparent legend panel
  )   

g
# ggsave(save_fname, g, width = w, height = h)
```



### point range
```{r}
# ----------------------------------------------------------------------------
#  Find common columns across dataframes for merging
# ----------------------------------------------------------------------------
fd.group.commoncolumn <- intersect(names(ukb_groupwise),
          names(groupwise_combined)
)

fd.subject.commoncolumn <- intersect(names(ukb_subjectwise),
          names(subjectwise_combined)
)
ukb.groupwise.common <- ukb_groupwise[fd.group.commoncolumn]
st.groupwise.common <- groupwise_combined[fd.group.commoncolumn]

ukb.subjectwise.common <- ukb_subjectwise[fd.subject.commoncolumn]
st.subjectwise.common <- subjectwise_combined[fd.subject.commoncolumn]


# ----------------------------------------------------------------------------
#  rstack dataframes across spacetop and ukbiobank
# ----------------------------------------------------------------------------
fd.groupwise.ukbst<- rbind(ukb.groupwise.common, st.groupwise.common)
fd.subjectwise.ukbst <- rbind(ukb.subjectwise.common, st.subjectwise.common)
fd.subjectwise.ukbst$task_ordered <- factor(fd.subjectwise.ukbst$task_factor, 
                             levels = c(  "UKB", "all tasks","social","shortvideo", "narratives","fractional","faces", "alignvideo"))
fd.groupwise.ukbst$task_ordered <- factor(fd.groupwise.ukbst$task_factor, 
                             levels = c(  "UKB", "all tasks","social","shortvideo", "narratives","fractional","faces", "alignvideo"))

# ----------------------------------------------------------------------------
#  plot
# ----------------------------------------------------------------------------
g <- plot_halfrainclouds_pointrange(
  fd.subjectwise.ukbst,
  fd.groupwise.ukbst,
  iv="task_ordered",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_mean",
  se = "ci",
  subject = "sub",
  ggtitle = "UKB and Spacetop FDmean across tasks",
  title="title",
  xlab="Framewise displacement (FD)",
  ylab="Task",
  taskname="spacetop",
  ylim=c(0,.9),
  w=5,
  h=5,
  dv_keyword="iqm",
  color=c("#333333", "#9300ff", "#6496BF", "#4f8b9e", "#3A7F7E", 
              # "#6a7272",
              "#996666","#c08658","#e6a74b", "#E18745", "#5A0B4D" ),
  border_levels = c("UKB"),
  border_color = "gray",
  save_fname="./fd_ukb_spacetop.png"
)


# ----------------------------------------------------------------------------
#  color palettes
# ----------------------------------------------------------------------------
# color = c("black","gray", "#6496BF","#3A7F7E","#996666","#E6A74B","#D85038", "#5A0B4D" )
# batlow


# ----------------------------------------------------------------------------
#  plot vertically and make transparent
# ----------------------------------------------------------------------------
g <- g + coord_flip() +
  ylim(0, .9) + theme_classic() + ylab("Framewise displacement (FD)") + xlab("Task") +
  theme(
    plot.title = element_text(size = 15),      # Adjust plot title size
    axis.title = element_text(size = 15),      # Adjust axis titles size
    axis.text = element_text(size = 12),       # Adjust axis text size
    legend.title = element_text(size = 15),    # Adjust legend title size
    legend.text = element_text(size = 10)      # Adjust legend text size
    
  ) +
  theme(text = element_text(size = 20)) +
  theme(
    panel.background = element_rect(fill = 'transparent'),     # transparent panel bg
    plot.background = element_rect(fill = 'transparent', color = NA),    # transparent plot bg
    panel.grid.major = element_blank(),                        # remove major gridlines
    panel.grid.minor = element_blank(),                        # remove minor gridlines
    legend.background = element_rect(fill = 'transparent'),    # transparent legend bg
    legend.box.background = element_rect(fill = 'transparent') # transparent legend panel
  )   

g
# ggsave(save_fname, g, width = w, height = h)
```

## Dvars
```{r}
df$task_factor <- factor(df$task)
subject <- "sub"
model_iv <- "task_factor"
dv <- "dvars_mean"
subjectwise <- meanSummary(df,c(subject, model_iv), dv)

groupwise <- summarySEwithin(
  data=subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv),
  idvar = subject
)

df$task_factor <- factor(df$task)
subject <- "sub"
# model_iv <- "task_factor"
dv <- "dvars_mean"
subjectwise_all <- meanSummary(df,c(subject), dv)
subjectwise_all$task_factor <- "all tasks"

groupwise_all <- summarySE(
  data=subjectwise_all,
  measurevar = "mean_per_sub",
  # withinvars = subject,
  # groupvars = subject
)
colnames(groupwise_all)
library(dplyr)
# groupwise_all <- groupwise_all %>% rename("task_factor" = ".id")
colnames(groupwise_all)[1] <- "task_factor"
groupwise_all$task_factor <- "all"

# Find common columns
group_common_columns <- intersect(names(groupwise), names(groupwise_all))

# Subset both data frames to only the common columns
df1_common <- groupwise[group_common_columns]
df2_common <- groupwise_all[group_common_columns]

# Row-bind the subsets
groupwise_combined <- rbind(df1_common, df2_common)
subjectwise_combined <- rbind(subjectwise, subjectwise_all)

```




```{r}

g <- plot_halfrainclouds_onefactor(
  subjectwise_combined,
  groupwise_combined,
  iv="task_factor",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_mean",
  se = "se",
  subject = "sub",
  ggtitle = "DVARS across tasks",
  title="title",
  xlab="DVARS",
  ylab="task",
  taskname="spacetop",
  ylim=c(20, 60),
  w=5,
  h=1,
  dv_keyword="iqm",
  color=c("#6496BF","#3A7F7E","#996666","#E6A74B","#D85038", "#5A0B4D", "black"),
  save_fname="./iqm.png"
)
g + coord_flip() + 
  ylim(20, 60) + theme_classic() + ylab("DVARS") + xlab("task")
```




## tsnr values

```{r}
tsnr <- read.csv("/Users/h/Documents/projects_local/spacetop-prep/spacetop_prep/qcplot/iqmvalues/tsnr_persub.csv")
```

```{r}
# ----------------------------------------------------------------------------
# summary stats for tasks (Non short video)
# ----------------------------------------------------------------------------
tsnr$task_factor <- factor(tsnr$task)
subject <- "sub"
model_iv <- "task_factor"
dv <- "median_value"
other.df <- tsnr[!tsnr$task_factor == "shortvideo",]
tsnr.subjectwise <- meanSummary(other.df,c(subject, model_iv), dv)

tsnr.groupwise <- summarySEwithin(
  data=tsnr.subjectwise,
  measurevar = "mean_per_sub",
  withinvars = c(model_iv),
  idvar = subject
)

# ----------------------------------------------------------------------------
# summary stats for short video
# ----------------------------------------------------------------------------
# only one value for short videos, summary stats between
shortvid.df <- tsnr[tsnr$task_factor == "shortvideo",]
tsnr.subjectwise.shortvideo  <- meanSummary(shortvid.df,c(subject), dv)
tsnr.subjectwise.shortvideo$sd <- sd(tsnr.subjectwise.shortvideo$mean_per_sub)
tsnr.subjectwise.shortvideo$task_factor <- "shortvideo"
tsnr.groupwise.shortvideo <- summarySE(
  data=tsnr.subjectwise.shortvideo,
  measurevar = "mean_per_sub",
  na.rm = TRUE
)
colnames(tsnr.groupwise.shortvideo)[1] <- "task_factor"
tsnr.groupwise.shortvideo$task_factor <- "shortvideo"

# ----------------------------------------------------------------------------
# summary stats for all tasks collapsed into one value
# ----------------------------------------------------------------------------
tsnr.subjectwise.all <- meanSummary(tsnr,c(subject), dv)
tsnr.subjectwise.all$task_factor <- "all tasks"

tsnr.groupwise.all <- summarySE(
  data=tsnr.subjectwise.all,
  measurevar = "mean_per_sub",
  # withinvars = subject,
  na.rm = TRUE
)
colnames(tsnr.groupwise.all)
library(dplyr)
colnames(tsnr.groupwise.all)[1] <- "task_factor"
tsnr.groupwise.all$task_factor <- "all tasks"


# ----------------------------------------------------------------------------
# Find common columns
# ----------------------------------------------------------------------------
group_common_columns <- intersect(
  intersect(names(tsnr.groupwise), names(tsnr.groupwise.all)),
  names(tsnr.groupwise.shortvideo)
)

# Subset both data frames to only the common columns
groupwise.common <- tsnr.groupwise[group_common_columns]
groupwisesv.common <- tsnr.groupwise.shortvideo[group_common_columns]
groupwise_all.common <- tsnr.groupwise.all[group_common_columns]

group_common_columns <- intersect(names(tsnr.subjectwise),
                                  names(tsnr.subjectwise.shortvideo))
subjectwise.tsnr.common <- tsnr.subjectwise[group_common_columns]
tsnr.subjectwise.shortvideo.common <- tsnr.subjectwise.shortvideo[group_common_columns]
##################################################
# Row-bind the subsets
groupwise_combined.tsnr <- rbind(groupwise.common, groupwisesv.common, groupwise_all.common)
subjectwise_combined.tsnr <- rbind(subjectwise.tsnr.common, tsnr.subjectwise.shortvideo.common, tsnr.subjectwise.all)
subjectwise_combined.tsnr$task_ordered <- factor(subjectwise_combined.tsnr$task_factor, 
                             levels = c( "all tasks", "social", "shortvideo", "narratives","fractional","faces", "alignvideo" ))
groupwise_combined.tsnr$task_ordered <- factor(groupwise_combined.tsnr$task_factor, 
                             levels = c( "all tasks", "social", "shortvideo", "narratives","fractional","faces", "alignvideo" ))
```
### boxplot
```{r}
g <- plot_halfrainclouds_onefactor(
  subjectwise_combined.tsnr,
  groupwise_combined.tsnr,
  iv="task_ordered",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_mean",
  se = "se",
  subject = "sub",
  ggtitle = "tSNR across tasks",
  title="title",
  xlab="tSNR",
  ylab="Task",
  taskname="spacetop",
  ylim=c(-300,300),
  w=5,
  h=5,
  dv_keyword="iqm",
  color=c( "#9300ff", "#6496BF", "#4f8b9e", "#3A7F7E", "#996666","#c08658","#e6a74b", "gray"),
 # color=c( "#6496BF", "#4f8b9e", "#3A7F7E", "#6a7272", "#996666","#c08658", "#E6A74B","#D85038", "#5A0B4D" ),
 border_levels = "all tasks",
 border_color = "purple",
  save_fname="./iqm.png"
  
)
#  "#6496bf"
# "#4f8b9e"
# "#3a7f7e"
# "#6a7272"
# "#996666"
# "#c08658"
# "#e6a74b"
g + coord_flip() + 
  ylim(0, 140) + theme_classic() + ylab("tSNR") + xlab("task") +
theme(
      plot.title = element_text(size = 20), # Adjust plot title size
      axis.title = element_text(size = 20), # Adjust axis titles size
      axis.text = element_text(size = 15),  # Adjust axis text size
      legend.title = element_text(size = 15), # Adjust legend title size
      legend.text = element_text(size = 10)  # Adjust legend text size
      
    ) +
theme(text = element_text(size = 20))
```


## Fig 2. pointrange tsnr
```{r}

 # "all tasks","social",
# levels = c( "all tasks", "social", "shortvideo", "narratives","fractional","faces", "alignvideo"))
g <- plot_halfrainclouds_pointrange(
  subjectwise_combined.tsnr,
  groupwise_combined.tsnr,
  iv="task_ordered",
  subjectwise_mean = "mean_per_sub",
  group_mean = "mean_per_sub_median",
  se = "ci",
  subject = "sub",
  ggtitle = "tSNR across tasks",
  title="title",
  xlab="tSNR",
  ylab="Task",
  taskname="spacetop",
  ylim=c(20,80),
  w=5,
  h=5,
  dv_keyword="iqm",
  # color = c("#333333","#66c2a5","#fc8d62","#8da0cb","#e78ac3","#a6d854","#ffd92f","#e5c494" ),
  color=c( "#333333", "#6496BF", "#4f8b9e", "#3A7F7E", "#996666","#c08658","#e6a74b", "gray"),
  # color=c("black", "#6496BF","#3A7F7E","#996666","#E6A74B","#D85038", "#5A0B4D" ),
  # border_levels = "all tasks", 
  # border_color = "gray",
  save_fname="./iqm.png"
)
# new_colors <- c("#6A9AC4", "#527D89", "#3A7F7E", "#996666", "#c08658", "#e6a74b")
# new_colors <- c("#6496BF", "#3A7F7E", "#5AAE61", "#996666", "#c08658", "#e6a74b")
# new_colors <- c("#5B9BD5", "#4682B4", "#8FBC8F", "#BC8F8F", "#DAA520", "#CD853F")
new_colors <- c("#5B9BD5", "#3A7F7E", "#8FBC8F", "#BC8F8F", "#DAA520", "#CD853F")
color=c( "#333333",  "#7DAFED"  "#3A7F7E","#6C9A75", "#996666","#c08658","#e6a74b", "gray")
g <- g + coord_flip() + 
  ylim(20,80) + theme_classic() + ylab("tSNR") + xlab("Task") +
  theme(
    plot.title = element_text(size = 15),      # Adjust plot title size
    axis.title = element_text(size = 15),      # Adjust axis titles size
    axis.text = element_text(size = 12),       # Adjust axis text size
    legend.title = element_text(size = 15),    # Adjust legend title size
    legend.text = element_text(size = 10)      # Adjust legend text size
    
  ) +
  theme(text = element_text(size = 20)) +
  theme(
    panel.background = element_rect(fill = 'transparent'),     # transparent panel bg
    plot.background = element_rect(fill = 'transparent', color = NA),    # transparent plot bg
    panel.grid.major = element_blank(),                        # remove major gridlines
    panel.grid.minor = element_blank(),                        # remove minor gridlines
    legend.background = element_rect(fill = 'transparent'),    # transparent legend bg
    legend.box.background = element_rect(fill = 'transparent') # transparent legend panel
  )  
g
ggsave("/Users/h/Dropbox/projects_adobe/spacetop_datapaper/iqm_tsnr.png", plot = g, width = 5, height = 4, dpi = 600)
```

